Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden, England and Wales

### 2020-08-27 reports/article.Rmd
Clarify excl of uncemented. Fix #56

We used data from the Swedish Hip Arthroplasty Register (SHAR) for model derivation and internal validation. The model was then validated externally on patients from England and Wales recorded in the National Joint Registry for England, Wales, Northern Ireland, the Isle of Man and the States of Guernsey (NJR). We focused on patients with cemented THA due to osteoarthritis. Cementation is the most common fixation technique used in Sweden, thus used as inclusion criteria to decrease heterogeneity. Only the last operated hip was accounted for in patients with bilateral THA (Figure \@ref(fig:flowchartshar)).[@Bulow2020]

>>>>

We used data from the Swedish Hip Arthroplasty Register (SHAR) for model derivation and internal validation. The model was then validated externally on patients from England and Wales recorded in the National Joint Registry for England, Wales, Northern Ireland, the Isle of Man and the States of Guernsey (NJR). We focused on patients with cemented THA due to osteoarthritis. ~~We thus excluded patients where either the femoral stem and/or the acetabular cup were uncemented (uncemented, hybrids and reverse hybrids).~~ Cementation is the most common fixation technique used in Sweden, thus used as inclusion criteria to decrease heterogeneity. Only the last operated hip was accounted for in patients with bilateral THA (Figure \@ref(fig:flowchartshar)).[@Bulow2020]
